---
title: "Drug Abuse & Rehabilitation in Singapore"
---

This page shall be updated to display trends surrounding *drug abuse and rehabilitation in Singapore* in due time.

## Information on Quantity of Controlled Drugs Siezed

```{r,echo=FALSE,eval=TRUE}
library(tidyverse)
quantity_drugs_seized <- read_csv("Informationonquantityofcontrolleddrugsseized.csv")
quantity_drugs_seized
```

## Inhalant Abusers Arrested by Status

```{r,echo=FALSE,eval=TRUE}
abusers_by_status <- read_csv("DataonInhalantAbusersArrestedByStatus.csv")
abusers_by_status
```

## Inhalant Abusers Arrested by Age

```{r,echo=FALSE,eval=TRUE}
abusers_by_age <- read_csv("DataonInhalantAbusersArrestedbyAgeGroup.csv")
abusers_by_age
```

## Inhalant Abusers Arrested by Gender

```{r,echo=FALSE,eval=TRUE}
abusers_by_gender <- read_csv("DataonInhalantAbusersArrestedByGender.csv")
abusers_by_gender
```

## Inhalant Abusers Arrested by Ethnicity

```{r,echo=FALSE,eval=TRUE}
abusers_by_ethnicity <- read_csv("DataonInhalantAbusersArrestedByEthnicGroup.csv")
abusers_by_ethnicity
```

## Population of Inmates in Drug Rehabilitation Centre

```{r,echo=FALSE,eval=TRUE}
inmates <- read_csv("PopulationofInmatesinDrugRehabilitationCentreDRC.csv")
inmates
```

## Population of Inmates in Drug Rehabilitation Centre by Age (Before 2020)

```{r,echo=FALSE,eval=TRUE}
inmates_by_age_before2020 <- read_csv("PopulationofInmatesinDrugRehabilitationCentreDRCbyAgeGroup20062020.csv")
inmates_by_age_before2020
```

## Population of Inmates in Drug Rehabilitation Centre by Age (After 2020)

```{r,echo=FALSE,eval=TRUE}
inmates_by_age_after2020 <- read_csv("PopulationofInmatesinDrugRehabilitationCentreDRCbyAgeGroup2020onwards.csv")
inmates_by_age_after2020
```

## Population of Inmates in Drug Rehabilitation Centre by Gender

```{r,echo=FALSE,eval=TRUE}
inmates_by_gender <- read_csv("PopulationofInmatesinDrugRehabilitationCentreDRCbyGender.csv")
inmates_by_gender
```

## Population of Inmates in Drug Rehabilitation Centre by Education Level

```{r,echo=FALSE,eval=TRUE}
inmates_by_education <- read_csv("PopulationofInmatesinDrugRehabilitationCentreDRCbyEducationLevel.csv")
inmates_by_education
```
